PANCHANGE_data_preprocessing

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
Fixed OCI-R script for NBR so it runs. One ID gets coerced to NA and there are some missing IDs we may want to find in the future.

    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from NBR prepandemic
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from NBR prepandemic

@@

@@

    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from NBR prepandemic
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from NBR prepandemic

@@

    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from NBR prepandemic

@@

    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from NBR prepandemic
    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from NBR prepandemic
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from NBR prepandemic

@@

    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from NBR prepandemic
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from NBR prepandemic

@@

@@

    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from NBR prepandemic
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from NBR prepandemic

@@

    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from NBR prepandemic

@@

    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from NBR prepandemic
    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from NBR prepandemic

>>>>

    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, ## Different from GLAD
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply,

@@

    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, ## Different from GLAD

@@

    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel,
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, 

@@

    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, 

@@

    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, 
    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, ## Different from GLAD 
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., 

@@

    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from GLAD
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1,

@@

    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, ## Different from GLAD

@@

    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, 
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, 

@@

    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, 

@@

    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, 
    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1,
